---
output: "Pratical Test 2022"
  md_document:
    variant: markdown_github
---

# Purpose

Purpose of this markdown to display all of the code.


```{r}

rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```


```{r}

# create a project
fmxdat::make_project(Open = T)
# File path = "C:/Masters Economics/Semester 1/Data Science/Practical Test"
# on the clipboard

# create folders for each Question
Texevier::create_template(directory = "C:/Masters Economics/Semester 1/Data Science/Practical2022/23365935",
                template_name = "Question1", build_project = TRUE, open_project = TRUE)
Texevier::create_template(directory = "C:/Masters Economics/Semester 1/Data Science/Practical2022/23365935",
                template_name = "Question2", build_project = TRUE, open_project = TRUE)
Texevier::create_template(directory = "C:/Masters Economics/Semester 1/Data Science/Practical2022/23365935",
                template_name = "Question3", build_project = TRUE, open_project = TRUE)
Texevier::create_template(directory = "C:/Masters Economics/Semester 1/Data Science/Practical2022/23365935",
                template_name = "Question4", build_project = TRUE, open_project = TRUE)
```


# Question 5

Application Categories that Generate the most Revenue.

From the graph below, one can see that the three categories of applications with the largest revenues on the Google Store are Lifestyle, Finance and Photography. This is likely due to the fact that these applications would appeal to the most users. I would issue caution, when considering developing a new app in any of these three categories as there is a large amount of competition and a new app may struggle to gain traction with incumbent apps having the first mover advantage.

```{r fig.height= 7}

# Use function to creat graph
graph_q5.1_func(df_data = df_q5.1_data,
                title = "Google Application Revenue",
                subtitle = "by Catergory",
                caption = "",
                xlabel = "Categories",
                ylabel = "Revenue")

```

\newpage

The table below, displays the mean statistics of price, number of installs, revenue, size per category. In terms of average price, the three most expensive categories are Finance, Lifestyle and Events.

```{r}
# print table function
Q5_table_func(df_data)

```

