---
title: 'Question 2: London Weather'
subtitle: Its Always Sunny in South Africa
documentclass: elsarticle
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
AddTitle: yes
Author1: Andrew Hyde^[__Contributions:__  \newline _The author would like to thank
  Nico Katzke for this template._]
CorrespAuthor_1: yes
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: Tex/harvard-stellenbosch-university.csl
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
Thesis_FP: no
abstract: |
  Reasons not to go to London according to data from UK National Weather Service.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
df_london <- read.csv("C:/Masters Economics/Semester 1/Data Science/Practical2022/23365935/Question2/data/London/london_weather.csv")

# source functions
library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))


```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Reasons not to go to London

## Low Average Temperature

London experiences lower average temperatures than South Africa. From the graph below, the average temperature in London has consistently fluctuates around 10 °C for over four decades.


```{r}
graph_q2.1_jitter_boxplot(df_data = df_q2.1_data,
                title = "Temperature over Time: London",
                subtitle = "Minimum and Maximum Temperature from 1979 to 2020",
                caption = "Data Source: UK National Weather Service ",
                xlabel = "Year",
                ylabel = "Temperature (°C)")

```

\newpage


## Few Hours of Sunlight per Month

London experiences very few hours of sunlight per month. In the last five years, the month with most number of hours of sunlight was May 2020, with approximately 330 hours in that month. On average, that is less than two hours of sunlight per day.

```{r}
graph_q2.2_func(df_data = df_q2.2_data,
                          title = "Hours of Sun in London over the last 5 years",
                          subtitle = "Hours of sun per month from 2016 to 2020",
                          caption = "Data Source: UK National Weather Service ",
                          xlabel = "year",
                          ylabel = "Hours of Sun")
```

\newpage


## It rains more than half the time

Consider the pie chart below, in 2020 it rained more than half the days in that year. In London there were at least 186 of rain, comparatively, Cape Town received 111 days of rain.

```{r}
graph_q2.3_func(df_data = df_q2.3_data,
                title = "Rain in London in 2020",
                subtitle = "The percentage of days with and without rain",
                caption = "Data Source: UK National Weather Service ",
                xlabel = "",
                ylabel = "")

```

