---
title: 'Question 5: Google'
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Andrew Hyde^[__Contributions:__  \newline _The author would like to thank
  Stack Overflow._]
Ref1: Stellenbosch University, South Africa
Email1: 23365935\@sun.ac.za
CorrespAuthor_1: yes
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: Tex/harvard-stellenbosch-university.csl
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
abstract: |
  Background information into App design trends.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# READ IN DATA
df_google <- read.csv("C:/Masters Economics/Semester 1/Data Science/Practical2022/23365935/Question5/data/googleplay/googleplaystore.csv")

# SOURCE FUNCTIONS
library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))


```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Application Categories that Generate the most Revemue.

From the graph below, one can see that the three categories of applications with the largest revenues on the Google Store are Lifestyle, Finance and Photography. This is likely due to the fact that these applications would appeal to the most users. I would issue caution, when considering developing a new app in any of these three categories as there is a large amount of competition and a new app may struggle to gain traction with incumbent apps having the first mover advantage.

```{r fig.height= 7}

# Use function to creat graph
graph_q5.1_func(df_data = df_q5.1_data,
                title = "Google Application Revenue",
                subtitle = "by Catergory",
                caption = "",
                xlabel = "Categories",
                ylabel = "Revenue")

```

\newpage

The table below, displays the mean statistics of price, number of installs, revenue, size per category. In terms of average price, the three most expensive categories are Finance, Lifestyle and Events.

```{r}
# print table function
Q5_table_func(df_data)

```



