---
title: 'Question 1: Covid'
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Andrew Hyde^[__Contributions:__  \newline _The author would like to thank
  Stack Overflow._]
Ref1: Stellenbosch University, South Africa
Email1: 23365935\@sun.ac.za
CorrespAuthor_1: yes
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: Tex/harvard-stellenbosch-university.csl
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
abstract: |
  New York Times to produce some statistics and figureson the evolution of the outbreakThe Covid-19 pandemic has wreaked havoc on many facets of our lives, and continue to affect travel, work and how people socially interact.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))


# Notice that as you are working in a .Rproj file (I am assuming you are) - the relative paths of your directories start at your specified root.
# This means that when working in a .Rproj file, you never need to use getwd() - it is assumed as your base root automatically.

# read in data

df_covid <- read.csv("C:/Masters Economics/Semester 1/Data Science/Practical2022/23365935/Question1/data/Covid/owid-covid-data.csv")

df_death_causes <- read.csv("C:/Masters Economics/Semester 1/Data Science/Practical2022/23365935/Question1/data/Covid/Deaths_by_cause.csv")

df_descriptions <- read.csv("C:/Masters Economics/Semester 1/Data Science/Practical2022/23365935/Question1/data/Covid/covid_data_description.csv")
getwd()
```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

Question 1.1

This compares the number of case and deaths linked to COVID per continent. From the graph below, one can see that Europe recorder the largest number of COVID cases and deaths. This may be due to there aging population, as advanced aged is certainly linked to comorbidities, which in turn may have resulted in increased cases compared to countries with a lower mean age.

```{r fig.height= 7}
graph_q1.1_func(df_data = df_q1.1_data,
                title = "Covid Cases and Deaths",
                subtitle = "Plot of Total Cases and Deaths per Continent",
                caption = "Data Source: Our World in Data",
                xlabel = "Continent",
                ylabel = "Per Million")

```

Question 1.2

This bar graph plots number of ICU patients and levels of poverty for the 10 poorest and 10 least poor countries as per extreme poverty. On average, countries with lower levels of poverty had comparatively fewer ICU patients that their wealthier counter parts. This is most like sue to a lake of ICU facilities in poorer countries. And had poorer had similar resources, there number of ICU patients would be very similar.

```{r}
graph_q1.2_func(df_data = df_q1.2_data,
                title = "Covid ",
                subtitle = "Plot of  Continent",
                caption = "Data Source: Our World in Data",
                xlabel = "Country",
                ylabel = "")


```

Question 1.3

The graphs below plots how the number of hospital beds and number of ICU admissions change will the onset of the pandemic per continent. From the graph, it appears that all continents lagged behind ICU admissions in increasing their hospitalization facilities. All except for Asia, who appear to have been able to make more facilities available quickly compared to the other continents. 

```{r}
graph_q1.3_func(df_data = df_q1.3_data,
                title = "Number of ICU Patients per million and Hospital Beds per thousand over time",
                subtitle = "per Continent",
                caption = "Data Source: Our World in Data",
                xlabel = "Continent",
                ylabel = "")
```


